Supplementary Analyses

### 2023-02-05 drafting_supplementary_analysis.Rmd
started drafting results section

---
title: "Who Cares about Morality"
author: "Mariola Paruzel-Czachura, Cillian McHugh"
date: "`r format(Sys.time(), '%d %B, %Y')`"
bibliography: "resources/bib/My Library.bib"
csl: "resources/bib/apa.csl"
output:
  bookdown::html_document2:
    fig_caption: yes
    toc: true
    toc_float:
      toc_collapsed: false
    toc_depth: 4
    number_sections: false
editor_options: 
  chunk_output_type: console
---

@@

df$country_lower <- tolower(df$country)
df$country_name <- countrycode(df$ISO3, origin = "iso3c", destination = "country.name")

@@

x <- df

table(x$sex3)
x <- x[which(x$sex3!="other"),]
x$sex3 <- droplevels(x$sex3)

t1 <- t.test(x$moral_identity_internal ~ x$sex3)
d1 <- cohen.d(x$moral_identity_internal, x$sex3)

d1$cohen.d[2]
sprintf("%.1f",mean(x$moral_identity_internal[which(x$sex3=='female')],na.rm=T))
sprintf("%.1f",sd(x$moral_identity_internal[which(x$sex3=='female')],na.rm=T))
sprintf("%.2f",t1$parameter)
sprintf("%.2f",t1$statistic)

t2 <- t.test(x$moral_identity_symbolic ~ x$sex3)
d2 <- cohen.d(x$moral_identity_symbolic, x$sex3)

Our first hypothesis was that women would have higher levels of internalization and symbolization than men. To test this we isolated the data for men and women from the main dataset. An independent samples t-test revealed that for the entire sample, women had higher internalization scores (*M* = `r sprintf("%.1f",mean(x$moral_identity_internal[which(x$sex3=='female')],na.rm=T))`, *SD* = `r sprintf("%.1f",sd(x$moral_identity_internal[which(x$sex3=='female')],na.rm=T))`), than men (*M* = `r sprintf("%.1f",mean(x$moral_identity_internal[which(x$sex3=='male')],na.rm=T))`, *SD* = `r sprintf("%.1f",sd(x$moral_identity_internal[which(x$sex3=='male')],na.rm=T))`), *t*(`r sprintf("%.2f",t1$parameter)`) = `r sprintf("%.2f",t1$statistic)`, *p* `r paste(p_report(t1$p.value))`, *d* = `r sprintf("%.2f", d1$cohen.d[2])`. Similarly, for symbolization, an independent samples t-test revealed that for the entire sample, women had higher scores (*M* = `r sprintf("%.1f",mean(x$moral_identity_symbolic[which(x$sex3=='female')],na.rm=T))`, *SD* = `r sprintf("%.1f",sd(x$moral_identity_symbolic[which(x$sex3=='female')],na.rm=T))`), than men (*M* = `r sprintf("%.1f",mean(x$moral_identity_symbolic[which(x$sex3=='male')],na.rm=T))`, *SD* = `r sprintf("%.1f",sd(x$moral_identity_symbolic[which(x$sex3=='male')],na.rm=T))`), *t*(`r sprintf("%.2f",t2$parameter)`) = `r sprintf("%.2f",t2$statistic)`, *p* `r paste(p_report(t2$p.value))`, *d* = `r sprintf("%.2f", d2$cohen.d[2])`.

x <- df

table(x$sex3)
x <- x[which(x$sex3!="other"),]
x$sex3 <- droplevels(x$sex3)

x$sex_01 <-  dplyr::recode(x$sex3,
               "male"="0"
              ,"female"="1")

model0 <- lmerTest::lmer(moral_identity_internal ~
                 #  sex_01
                 # * age
                  + (1|country)
                , data = x
                # , contrasts = list(sex3 = contr.sum, valence = contr.sum )
            )

model1 <- lmerTest::lmer(moral_identity_internal ~
                    sex_01
                 # * age
                  + (1|country)
                , data = x
               # , contrasts = list(sex_01 = contr.sum)
            )
summary(model1)
anova(model0,model1)

summary(model1)
anova(model1)
results_anova <- as.data.frame(anova(model0,model1))
results_anova
results_anova$Chisq[2]
results_anova$Df
p1 <- results_anova$`Pr(>Chisq)`[2]
p_report(p1)
#p_report(results_anova$`Pr(>Chisq)`)[2]
results_anova$AIC
summary_model1 <- summary(model1)
summary_model1
results_coef <- as.data.frame(summary_model1$coefficients)
results_coef

aov1 <- anova(model1)

f3a <- aov1$`F value`[1]
p3a <- aov1$`Pr(>F)`[1]

results_coef$Estimate[2]
results_coef$`Std. Error`[2]
results_coef$df[2]
t1 <- results_coef$`t value`[2]
p2 <- results_coef$`Pr(>|t|)`[2]

#QuantPsyc::lm.beta(results_coef)
anova(model1)
```

@@

means_fun <- function(x){
  mean(x$moral_identity_internal)
}
lapply(x, means_fun)
sd_fun <- function(x){
  sd(x$moral_identity_internal)
}
lapply(x, sd_fun)

all_t_ps <- function(t){
  t$p.value
}
ps_for_table <- lapply((lapply(all_t_tests, all_t_ps)), p_report)

@@

@@

@@

We conducted a linear-mixed-effects model to test for gender differences in internalization when participants are nested within country. Our outcome measure was internalization and our predictor variable was binary gender (coded as 0 = *male*; 1 = *female*); we allowed intercepts to vary by country.
Overall, the model significantly predicted internalization, and provided a better fit for the data than the baseline model,
$\chi$^2^(`r results_anova$Df[2]`) = `r sprintf("%.2f",results_anova$Chisq[2])`), *p* `r paste(p_report(p1))`. 
There was a significant main effect for gender,
*F*(`r aov1$NumDF[1]`, `r sprintf("%.2f",round(aov1$DenDF[1],digits=2))`) = 
`r sprintf("%.2f",f3a)`, *p* `r paste(p_report(p3a))`;
with a significant positive association between being female and higher internalization scores, $b$ = `r sprintf("%.2f",results_coef$Estimate[2])`,
*t*(`r sprintf("%.2f",results_coef$df[2])`) = 
`r sprintf("%.2f",t1)`
, *p* `r paste(p_report(p2))`.
We conducted a series of independent-samples t-tests to test for gender differences in internalization across all countries. We found this effect across `r total_sig` countries (see Supplementary Materials Table S_X).

@@

x <- df

table(x$sex3)
x <- x[which(x$sex3!="other"),]
x$sex3 <- droplevels(x$sex3)

x$sex_01 <-  dplyr::recode(x$sex3,
               "male"="0"
              ,"female"="1")

model0 <- lmerTest::lmer(moral_identity_symbolic ~
                 #  sex_01
                 # * age
                  + (1|country)
                , data = x
                # , contrasts = list(sex3 = contr.sum, valence = contr.sum )
            )

model1 <- lmerTest::lmer(moral_identity_symbolic ~
                    sex_01
                 # * age
                  + (1|country)
                , data = x
              #  , contrasts = list(sex_01 = contr.sum)
            )
summary(model1)
anova(model0,model1)

summary(model1)
anova(model1)
results_anova <- as.data.frame(anova(model0,model1))
results_anova
results_anova$Chisq[2]
results_anova$Df
p1 <- results_anova$`Pr(>Chisq)`[2]
p_report(p1)
#p_report(results_anova$`Pr(>Chisq)`)[2]
results_anova$AIC
summary_model1 <- summary(model1)
summary_model1
results_coef <- as.data.frame(summary_model1$coefficients)
results_coef

aov1 <- anova(model1)

f3a <- aov1$`F value`[1]
p3a <- aov1$`Pr(>F)`[1]

results_coef$Estimate[2]
results_coef$`Std. Error`[2]
results_coef$df[2]
t1 <- results_coef$`t value`[2]
p2 <- results_coef$`Pr(>|t|)`[2]

#QuantPsyc::lm.beta(results_coef)
anova(model1)
```

@@

@@

all_t_ps <- function(t){
  t$p.value
}
ps_for_table <- lapply((lapply(all_t_tests, all_t_ps)), p_report)

@@

We conducted another linear-mixed-effects model to test for gender differences in symbolization when participants are nested within country. Our outcome measure was symbolization and our predictor variable was binary gender (coded as 0 = *male*; 1 = *female*); we allowed intercepts to vary by country.
Overall, the model significantly predicted symbolization, and provided a better fit for the data than the baseline model,
$\chi$^2^(`r results_anova$Df[2]`) = `r sprintf("%.2f",results_anova$Chisq[2])`), *p* `r paste(p_report(p1))`. 
There was a significant main effect for gender,
*F*(`r aov1$NumDF[1]`, `r sprintf("%.2f",round(aov1$DenDF[1],digits=2))`) = 
`r sprintf("%.2f",f3a)`, *p* `r paste(p_report(p3a))`;
with a significant positive association between being female and higher symbolization scores, $b$ = `r sprintf("%.2f",results_coef$Estimate[2])`,
*t*(`r sprintf("%.2f",results_coef$df[2])`) = 
`r sprintf("%.2f",t1)`
, *p* `r paste(p_report(p2))`.
We conducted a series of independent-samples t-tests to test for gender differences in symbolization across all countries. We found this effect across `r total_sig` countries (see Supplementary Materials Table S_X).

```{r internalizationPlot}

x <- df[which(df$sex3=="male"|df$sex3=="female"),]
x$sex3 <- droplevels(x$sex3)

df1 <- x

df1_male <- df1[which(df1$sex3=="male"),]
df1_female <- df1[which(df1$sex3=="female"),]

internal_mean_sd <- function(x){
  z <- x
  z$mean <- mean(z$moral_identity_internal, na.rm=T)
  z$sd <- sd(z$moral_identity_internal, na.rm=T)
  z
}

df1 <- rbind.data.frame(
  internal_mean_sd(df1_female),
  internal_mean_sd(df1_male)
)

df1$sex3 <- dplyr::recode(df1$sex3
                           , "male" = "Male"
                           , "female" = "Female")

g1 <- ggplot(df1,aes(x=sex3,y=moral_identity_internal))+
  geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.001, color="lightgrey")+
  geom_violin(fill = NA) +
  #ggforce::geom_sina(size=.01)+
  # geom_sina(shape=16
  #           , position=position_jitter(height=.25,width=0)
  #           , size=.000001
  #           , color="dark grey"
  #           ,jitter_y=F
  # )+
  geom_boxplot(width=0.1, outlier.shape = NA, color='grey')+
  geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.06,
               position=position_dodge(0.05), color="#5a5a5a")+
  stat_summary(fun=mean, geom="point", shape=16, size=2)+
  # stat_summary(geom = "linerange",
  #   fun.data = mean_sdl, 
  #   fun.args = list(mult = 1),
  #   colour = "black"
  # )+
  xlab("Gender")+
  ylab("Internalization")+  
  #geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.01, color="dark grey")
  theme_bw() +
  theme(panel.border = element_blank(),
        axis.line = element_line(size = .2),
        strip.background  = element_blank(),
        panel.grid = element_blank(),
        plot.title=element_text(#family="Times",
          size=12
        ),
        #legend.position="right",
        legend.text=element_text(#family="Times",
          size=8
        ),
        legend.title=element_text(#family="Times",
          size=10
        ),
        axis.text=element_text(#family="Times",
          colour = "black",
          size=8
        ),
        axis.ticks.x = element_blank(),
        axis.title=element_text(#family="Times",
          size=12
        ),
        strip.text=element_text(#family = "Times",
          size = 12
        ),
        # strip.background = element_rect(fill = "white"),
        legend.position="none")

#g1
```

```{r symbolizationPlot}

symbolic_mean_sd <- function(x){
  z <- x
  z$mean <- mean(z$moral_identity_symbolic, na.rm=T)
  z$sd <- sd(z$moral_identity_symbolic, na.rm=T)
  z
}

df1 <- rbind.data.frame(
  symbolic_mean_sd(df1_female),
  symbolic_mean_sd(df1_male)
)

df1$sex3 <- dplyr::recode(df1$sex3
                           , "male" = "Male"
                           , "female" = "Female")

# df1 <- df
g2 <- ggplot(df1,aes(x=sex3,y=moral_identity_symbolic))+
  geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.001, color="lightgrey")+
  geom_violin(fill = NA) +
  #ggforce::geom_sina(size=.01)+
  # geom_sina(shape=16
  #           , position=position_jitter(height=.25,width=0)
  #           , size=.000001
  #           , color="dark grey"
  #           ,jitter_y=F
  # )+
  #geom_quasirandom(size=.1)+
  geom_boxplot(width=0.1, outlier.shape = NA, color='grey')+
  geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.06,
               position=position_dodge(0.05), color="#5a5a5a")+
  stat_summary(fun=mean, geom="point", shape=16, size=2)+
  # stat_summary(geom = "linerange",
  #   fun.data = mean_sdl, 
  #   fun.args = list(mult = 1),
  #   colour = "black"
  # )+
  xlab("Gender")+
  ylab("Symbolization")+  
  #geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.01, color="dark grey")
  theme_bw() +
  theme(panel.border = element_blank(),
        axis.line = element_line(size = .2),
        strip.background  = element_blank(),
        panel.grid = element_blank(),
        plot.title=element_text(#family="Times",
          size=12
        ),
        #legend.position="right",
        legend.text=element_text(#family="Times",
          size=8
        ),
        legend.title=element_text(#family="Times",
          size=10
        ),
        axis.text=element_text(#family="Times",
          colour = "black",
          size=8
        ),
        axis.ticks.x = element_blank(),
        axis.title=element_text(#family="Times",
          size=12
        ),
        strip.text=element_text(#family = "Times",
          size = 12
        ),
        # strip.background = element_rect(fill = "white"),
        legend.position="none")

#g2
```

```{r, combinePlots, include=FALSE}
figure <- ggarrange(g1
                    , g2
                    #,labels = c("A")
                    , ncol = 1
                    , nrow = 2
                    #, widths = c(0.485, 0.5)
)
figure
```

```{r, meanSymbolizationGender,include=TRUE}
suppressWarnings(print(figure))

@@

### symb

@@

model1 <- lmerTest::lmer(moral_identity_internal ~
                    sex3
                 # * age
                  + (1|country)
                , data = x
                , contrasts = list(sex3 = contr.sum, valence = contr.sum )
            )
summary(model1)
anova(model1)

>>>>

---
title: "Supplementary Analyses"
author: "Mariola Paruzel-Czachura, Cillian McHugh"
date: "`r format(Sys.time(), '%d %B, %Y')`"
bibliography: "resources/bib/My Library.bib"
csl: "resources/bib/apa.csl"
output:
  bookdown::html_document2:
    fig_caption: yes
    toc: true
    toc_float:
      toc_collapsed: false
    toc_depth: 4
    number_sections: false
editor_options: 
  chunk_output_type: console
---

@@

df$country_lower <- tolower(df$country)
df$country_name <- countrycode(df$ISO3, origin = "iso3c", destination = "country.name")
```

## Internalization

@@

ps <- function(y){
  y <- round(y, digits = 3)
  if(as.numeric(sqrt( y*y) ) <.001) print(paste0("<", " ", ".001","**"), quote = FALSE)
  else if(as.numeric(sqrt( y*y) ) <.05) print(paste0(sub("^(-?)0.", "\\1.", sprintf("%.3f", 
        y, quote = FALSE)),"*"))
  else print(sub("^(-?)0.", "\\1.", sprintf("%.3f", 
        y)))}

@@

# Means and Standard Deviations
means_fun <- function(x){
  mean(x$moral_identity_internal)
}
lapply(x, means_fun)
sd_fun <- function(x){
  sd(x$moral_identity_internal)
}
lapply(x, sd_fun)

N_fun <- function(x){
  length(x$sex3)
}
total_Ns <- lapply(x, N_fun)

# Statistics for table
# Cohen's d
cohens_d_fun <- function(x){
  cohen.d(x$moral_identity_symbolic, x$sex3)
}
all_ds <- lapply(x, cohens_d_fun)
show_d_fun <- function(x){
  x$cohen.d[2]
}
ds_for_table <- lapply(all_ds, show_d_fun)

# t statistic
all_t_stats <- function(t){
  t$statistic
}
ts_for_table <- lapply(all_t_tests, all_t_stats)

# df
all_t_df <- function(t){
  t$parameter
}
df_for_table <- lapply(all_t_tests, all_t_df)

# p value
all_t_ps <- function(t){
  t$p.value
}
ps_for_table <- lapply((lapply(all_t_tests, all_t_ps)), ps)

sum(unlist(lapply(all_t_tests, all_t_ps))<.05)

@@

x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
male_means <- lapply(x, means_fun)
male_sds <- lapply(x, sd_fun)
male_Ns <- lapply(x, N_fun)

@@

x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
female_means <- lapply(x, means_fun)
female_sds <- lapply(x, sd_fun)
female_Ns <- lapply(x, N_fun)

@@

### Internalization Ns

```{r}
#### Total Ns
x <- df[which(df$sex3=="male"
              |df$sex3=="female"
              ),]
x$sex3 <- droplevels(x$sex3)

# and remove missing again
sum(is.na(x$moral_identity_internal))
x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
total_Ns <- lapply(x, N_fun)

#### Ns for Males 
# re-load ungrouped data #
x <- df[which(df$sex3=="male"
              #|df$sex3=="female"
              ),]
x$sex3 <- droplevels(x$sex3)

# and remove missing again
sum(is.na(x$moral_identity_internal))
x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
male_Ns <- lapply(x, N_fun)

#### Ns for Females
# re-load ungrouped data #
x <- df[which(df$sex3=="female"
              #|df$sex3=="female"
              ),]
x$sex3 <- droplevels(x$sex3)
# and remove missing again
sum(is.na(x$moral_identity_internal))
x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
female_Ns <- lapply(x, N_fun)

test <- 
  cbind.data.frame(do.call(rbind, total_Ns)
                 ,do.call(rbind, female_Ns)
                 ,do.call(rbind, male_Ns))

test <- `colnames<-`(test, c("Total N","n Female","N male"))

loop_exclusions_fun <- function(x){
  if(rownames(test)[x] %in% exclusions) print(paste0(rownames(test)[x],"*"),quote = FALSE)
  else print(rownames(test)[x])
  }

rownames(test) <-  unlist(lapply(1:length(rownames(test)), loop_exclusions_fun))
test
test <- test[order(rownames(test) ),]

```{r include=TRUE}

apa_table(
  test
  , align = c("c", "c", "c")
  , caption = "Total samples for each country for Internalization analysis"
  , note = "* = sample too small to be included in analysis below")

### Internalization Table

@@

test <- 
  cbind.data.frame(
     round(do.call(rbind, female_means),digits=2)
    ,round(do.call(rbind, female_sds),digits=2)
    ,round(do.call(rbind, male_means),digits=2)
    ,round(do.call(rbind, female_sds),digits=2)
    ,round(do.call(rbind, ts_for_table),digits=2)
    ,round(do.call(rbind, df_for_table),digits=2)
    ,do.call(rbind, ps_for_table)
    ,round(do.call(rbind, ds_for_table),digits=2)
    )

test <- `colnames<-`(test, c("mean F","SD F","mean M", "SD M", "t","df","p","d"))
test

x <- df[which(df$sex3=="male"
              |df$sex3=="female"
              ),]
x$sex3 <- droplevels(x$sex3)

# and remove missing again
sum(is.na(x$moral_identity_internal))
x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
total_Ns <- lapply(x, N_fun)

P_R <- x$`Puerto Rico`
P_R <- 
  `rownames<-`(
    `colnames<-`(
      as.data.frame(
        rbind(
          # c("mean F","SD F","mean M", "SD M", "t","df","p","d")
          # ,
          c(
            P_R$moral_identity_internal[which(P_R$sex3=="male")]
            ,"-"
            ,P_R$moral_identity_internal[which(P_R$sex3=="female")]
            ,"-"
            ,"-"
            ,"-"
            ,"-"
            ,"-"))),
      c("mean F","SD F","mean M", "SD M", "t","df","p","d"))
    ,c("Peurto Rico"))

test <- rbind(test[1:49,],P_R,test[50:length(test$`mean F`),])
test <- test[order(rownames(test) ),]

```{r include=TRUE}

apa_table(
  test
  , align = c("l", "l", "c", "c", "c", "c", "c", "c", "c", "c")
  , caption = "Gender differences in Internalization for each Country"
  , note = "* = sig. at p < .05; ** = sig. at p < .001")

## Symbolization

@@

ps <- function(y){
  y <- round(y, digits = 3)
  if(as.numeric(sqrt( y*y) ) <.001) print(paste0("<", " ", ".001","**"), quote = FALSE)
  else if(as.numeric(sqrt( y*y) ) <.05) print(paste0(sub("^(-?)0.", "\\1.", sprintf("%.3f", 
        y, quote = FALSE)),"*"))
  else print(sub("^(-?)0.", "\\1.", sprintf("%.3f", 
        y)))}

@@

all_t_ps <- function(t){
  t$p.value
}
ps_for_table <- lapply((lapply(all_t_tests, all_t_ps)), ps)

@@

### Symbolization Ns

```{r}
#### Total Ns
x <- df[which(df$sex3=="male"
              |df$sex3=="female"
              ),]
x$sex3 <- droplevels(x$sex3)

# and remove missing again
sum(is.na(x$moral_identity_symbolic))
x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
total_Ns <- lapply(x, N_fun)

#### Ns for Males 
# re-load ungrouped data #
x <- df[which(df$sex3=="male"
              #|df$sex3=="female"
              ),]
x$sex3 <- droplevels(x$sex3)

# and remove missing again
sum(is.na(x$moral_identity_symbolic))
x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
male_Ns <- lapply(x, N_fun)

#### Ns for Females
# re-load ungrouped data #
x <- df[which(df$sex3=="female"
              #|df$sex3=="female"
              ),]
x$sex3 <- droplevels(x$sex3)
# and remove missing again
sum(is.na(x$moral_identity_symbolic))
x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
female_Ns <- lapply(x, N_fun)

test <- 
  cbind.data.frame(do.call(rbind, total_Ns)
                 ,do.call(rbind, female_Ns)
                 ,do.call(rbind, male_Ns))

test <- `colnames<-`(test, c("Total N","n Female","N male"))

loop_exclusions_fun <- function(x){
  if(rownames(test)[x] %in% exclusions) print(paste0(rownames(test)[x],"*"),quote = FALSE)
  else print(rownames(test)[x])
  }

rownames(test) <-  unlist(lapply(1:length(rownames(test)), loop_exclusions_fun))
test
test <- test[order(rownames(test) ),]

@@

```{r include=TRUE}

apa_table(
  test
  , align = c("c", "c", "c")
  , caption = "Total samples for each country for Symbolization analysis"
  , note = "* = sample too small to be included in analysis below")

### Symbolization Table

test <- 
  cbind.data.frame(
     round(do.call(rbind, female_means),digits=2)
    ,round(do.call(rbind, female_sds),digits=2)
    ,round(do.call(rbind, male_means),digits=2)
    ,round(do.call(rbind, female_sds),digits=2)
    ,round(do.call(rbind, ts_for_table),digits=2)
    ,round(do.call(rbind, df_for_table),digits=2)
    ,do.call(rbind, ps_for_table)
    ,round(do.call(rbind, ds_for_table),digits=2)
    )

test <- `colnames<-`(test, c("mean F","SD F","mean M", "SD M", "t","df","p","d"))
test

x <- df[which(df$sex3=="male"
              |df$sex3=="female"
              ),]
x$sex3 <- droplevels(x$sex3)

# and remove missing again
sum(is.na(x$moral_identity_symbolic))
x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
total_Ns <- lapply(x, N_fun)

P_R <- x$`Puerto Rico`
P_R <- 
  `rownames<-`(
    `colnames<-`(
      as.data.frame(
        rbind(
          # c("mean F","SD F","mean M", "SD M", "t","df","p","d")
          # ,
          c(
            P_R$moral_identity_symbolic[which(P_R$sex3=="male")]
            ,"-"
            ,P_R$moral_identity_symbolic[which(P_R$sex3=="female")]
            ,"-"
            ,"-"
            ,"-"
            ,"-"
            ,"-"))),
      c("mean F","SD F","mean M", "SD M", "t","df","p","d"))
    ,c("Peurto Rico"))

test <- rbind(test[1:49,],P_R,test[50:length(test$`mean F`),])
test <- test[order(rownames(test) ),]

```{r include=TRUE}

apa_table(
  test
  , align = c("l", "l", "c", "c", "c", "c", "c", "c", "c", "c")
  , caption = "Gender differences in Symbolization for each Country"
  , note = "* = sig. at p < .05; ** = sig. at p < .001")

# Overview

# Testing for Country Effects

## Internalization

# start building the model
## first test if country should be included

# no country
interceptOnly <-gls(moral_identity_internal ~ 1
                    , data = df
                    , method = "ML"
                    , na.action = na.exclude)
summary(interceptOnly)

# country included
randomInterceptOnly <-lme(moral_identity_internal ~ 1
                          , data = df
                          , random = ~1|country
                          , method = "ML"
                          , na.action = na.exclude)
summary(randomInterceptOnly)

LL_d <- logLik(interceptOnly)*-2 - logLik(randomInterceptOnly)*-2
aov <- anova(interceptOnly, randomInterceptOnly)
country_p <- aov$`p-value`[2]

Initial testing revealed that for Internalization, allowing intercepts to vary with Country significantly improved the predictive power of the model $\chi$^2^(`r round(aov$df[2]-aov$df[1], digits=2)`) = `r round(aov$L.Ratio[2],digits=2)`, *p* `r paste(p_report(country_p))`.

```{r}
test <- 
  do.call(
    rbind,
    tapply(df$moral_identity_internal, df$ISO3, descriptives)
    )

descriptives(df$moral_identity_internal)

test[order(-test$mean), ]
country_order <- rownames(test[order(-test$mean), ])
```

```{r, internalizationCountry, include=TRUE}
apa_table(
  test
  , caption = "Internalization basic descriptives by Country")
```

```{r}
# https://www.r-bloggers.com/2019/03/all-around-the-world-maps-and-flags-in-r/
df$flag_location <- rep(-1)

test1 <- test[order(-test$mean), ]
test1$country1 <- rownames(test1)
test1$position <- c(11:(10+length(test1$country1)))
test1$ISO3 <- test1$country1
test1$position_country <- paste0(test1$position,test1$country1)
df1 <- left_join(df, test1, by = "ISO3")
```

g <- ggplot(df1,aes(x=position_country,y=moral_identity_internal))+
  #geom_violin() +
  stat_summary(fun=mean, geom="point", shape=23, size=2)+
  geom_boxplot(width=0.1, outlier.shape = NA)+
  xlab("Country")+
  ylab("Internalization")+
  geom_jitter(shape=16, position=position_jitter(0.15), size=.1, color="dark grey")+
  geom_axis_flags(breaks = df1$position_country,
                   labels = df1$ISO3,
                   country_icons = df1$ISO3,
                   axis = "x",
                    width = 20,
                   # lineheight = 2,
                   # fontface = "bold"
  )
```

<div class=superbigimage>
```{r, meanInternalization,include=TRUE,fig.width=20,fig.height=6}
suppressWarnings(print(g))

</div>
## Symbolization

```{r}
# 
# # start building the model
# ## first test if country should be included
# 
# # no country
# interceptOnly <-gls(moral_identity_symbolic ~ 1
#                     , data = df
#                     , method = "ML"
#                     , na.action = na.exclude)
# summary(interceptOnly)
# 
# # country included
# randomInterceptOnly <-lme(moral_identity_symbolic ~ 1
#                           , data = df
#                           , random = ~1|country
#                           , method = "ML"
#                           , na.action = na.exclude)
# summary(randomInterceptOnly)
# 
# LL_d <- logLik(interceptOnly)*-2 - logLik(randomInterceptOnly)*-2
# aov <- anova(interceptOnly, randomInterceptOnly)
# country_p <- aov$`p-value`[2]

Initial testing revealed that for Symbolization, allowing intercepts to vary with Country significantly improved the predictive power of the model $\chi$^2^(`r round(aov$df[2]-aov$df[1], digits=2)`) = `r round(aov$L.Ratio[2],digits=2)`, *p* `r paste(p_report(country_p))`.

```{r}
test <- 
  do.call(
    rbind,
    tapply(df$moral_identity_symbolic, df$ISO3, descriptives)
    )

descriptives(df$moral_identity_symbolic)

test[order(-test$mean), ]
country_order <- rownames(test[order(-test$mean), ])
```

```{r, symbolizationCountry, include=TRUE}
apa_table(
  test
  , caption = "Symbolization basic descriptives by Country")
```

```{r}
# https://www.r-bloggers.com/2019/03/all-around-the-world-maps-and-flags-in-r/
df$flag_location <- rep(-1)

test1 <- test[order(-test$mean), ]
test1$country1 <- rownames(test1)
test1$position <- c(11:(10+length(test1$country1)))
test1$ISO3 <- test1$country1
test1$position_country <- paste0(test1$position,test1$country1)
df1 <- left_join(df, test1, by = "ISO3")
```

g <- ggplot(df1,aes(x=position_country,y=moral_identity_symbolic))+
  #geom_violin() +
  stat_summary(fun=mean, geom="point", shape=23, size=2)+
  geom_boxplot(width=0.1, outlier.shape = NA)+
  xlab("Country")+
  ylab("Symbolization")+
  geom_jitter(shape=16, position=position_jitter(0.15), size=.1, color="dark grey")+
  geom_axis_flags(breaks = df1$position_country,
                   labels = df1$ISO3,
                   country_icons = df1$ISO3,
                   axis = "x",
                    width = 20,
                   # lineheight = 2,
                   # fontface = "bold"
  )
```

<div class=superbigimage>
```{r, meanSymbolization,include=TRUE,fig.width=20,fig.height=6}
suppressWarnings(print(g))

</div>

# Gender Differences

```{r}
test <- 
  do.call(
    rbind,
    tapply(df$moral_identity_internal, df$sex3, descriptives)
    )

descriptives(df$moral_identity_internal)

test[order(-test$mean), ]
country_order <- rownames(test[order(-test$mean), ])
```

```{r, internalizationgender, include=TRUE}
apa_table(
  test
  , caption = "Internalization basic descriptives by Gender")
```

```{r}
df1 <- df
g <- ggplot(df1,aes(x=sex3,y=moral_identity_internal))+
  geom_violin() +
  #ggforce::geom_sina(size=.01)+
  stat_summary(fun=mean, geom="point", shape=23, size=2)+
  geom_boxplot(width=0.1, outlier.shape = NA)+
  xlab("Gender")+
  ylab("Internalization")+  
  geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.01, color="dark grey")

g
```

```{r, meanInternalizationGender,include=TRUE}
suppressWarnings(print(g))

```{r}
test <- 
  do.call(
    rbind,
    tapply(df$moral_identity_symbolic, df$sex3, descriptives)
    )

descriptives(df$moral_identity_symbolic)

test[order(-test$mean), ]
country_order <- rownames(test[order(-test$mean), ])
```

```{r, symbolizationgender, include=TRUE}
apa_table(
  test
  , caption = "Symbolization basic descriptives by Gender")
```

```{r}
df1 <- df
g <- ggplot(df1,aes(x=sex3,y=moral_identity_symbolic))+
  geom_violin() +
  #ggforce::geom_sina(size=.01)+
  stat_summary(fun=mean, geom="point", shape=23, size=2)+
  geom_boxplot(width=0.1, outlier.shape = NA)+
  xlab("Gender")+
  ylab("Symbolization")+  
  geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.01, color="dark grey")

g
```

```{r, meanSymbolizationGender,include=TRUE}
suppressWarnings(print(g))

@@

model1 <- lmerTest::lmer(moral_identity_internal ~
                    sex3
                  * age
                  + (1|country)
                , data = x
                , contrasts = list(sex3 = contr.sum, valence = contr.sum )
            )
summary(model1)
anova(model1)
